{\color {red}better title eventually}

### 2015-05-11 cs261n-paper/paper.tex
Move up censorship subsection.
wrote some intro

\title{better title eventually}
\author{Linda N. Lee, David Fifield\\
University of California, Berkeley, \{lnl, fifield\}@cs.berkeley.edu
}
\maketitle

% is the abstract missing some oomph? 
% I don't know how much the storyline is showing through.. or what we are testing. 
\begin{abstract}
\indent \indent Tor has grown beyond its original purpose and has  since become an important 
Internet circumvention tool. We specifically examine it usability as a censorship circumvention tool, 
an essential facet for adoption and use.  We focus our analysis on the connection configuration dialog of 
Tor browser, as censorship circumvention requires correct transport configurations. 
This study is aimed at evaluating if and how easily users can circumvent censorship using Tor Browser,
isolating specific browser features to study in the process.  To this end, we present the design of
 a large-scale user study examining hundreds of users  on how they navigate Tor's configuration wizard to complete seven browsing tasks in three different adversarial settings. The experiment is scheduled for August 2015.
\end{abstract}

@@

\subsection{What is Required of Users} %%%
\indent \indent For users to circumvent censorship in their resident countries, they will need to 
configure Tor to set up a proxy, bridge, or both. The requirement of the user will vary on their censorship
environment, specifically, if they need to conceal the fact that they are using Tor or if Tor entry nodes 
have been blocked by the government.

There is a configuration wizard to help guide users through setting up their connection, but our hypothesis is that the average user will not easily be able to configure Tor correctly in these adverse settings, as they require the user to provide IP addresses of proxies or bridges to use. The goal of our experiment is to see how successful users are at carrying out common browsing tasks in an adversarial setting using Tor.

{\color {red} Talk about the basic methods of censoring, and how it differs 
around the world, which sites are targeted, etc.

Scope the paper here. Talk about how we are not up Cuba-like adversaries. }

>>>>

\title{{\color {red}better title eventually}}
\author{Linda N. Lee, David Fifield\\
University of California, Berkeley, \{lnl, fifield\}@cs.berkeley.edu
}
\maketitle

\begin{abstract}
\indent \indent Tor has grown beyond its original purpose and has  since become an important 
Internet circumvention tool. We specifically examine it usability as a censorship circumvention tool, 
an essential facet for adoption and use.  We focus our analysis on the connection configuration dialog of 
Tor browser, as censorship circumvention requires correct transport configurations. 
This study is aimed at evaluating if and how easily users can circumvent censorship using Tor Browser,
isolating specific browser features to study in the process.  To this end, we present the design of
 a large-scale user study examining hundreds of users  on how they navigate Tor's configuration wizard to complete seven browsing tasks in three different adversarial settings. The experiment is scheduled for August 2015.
\end{abstract}

@@

\subsection{What is Required of Users}
\indent \indent For users to circumvent censorship in their resident countries, they will need to 
configure Tor to set up a proxy, bridge, or both. The requirement of the user will vary on their censorship
environment, specifically, if they need to conceal the fact that they are using Tor or if Tor entry nodes 
have been blocked by the government. There is a configuration wizard to help guide users through setting up their connection, but they require the user to provide IP addresses of proxies or bridges to use.

The end user generally does not care about the details of the 
censorship environment, and how the censorship is implemented; rather, they care about how to get
to the website of their choice. In the wild, users may choose to get the required information in a variety 
of ways, including reading online manuals on how to configure Tor, finding out information through word of mouth, 
or figuring out correct configurations themselves by trial and error.  We cannot accurately simulate the effects
of these localized effects during our experiment.

However, we are testing the usability, and therefore comprehension and user-friendliness, of the Tor configuration 
dialog, which will require users in the most strict censorship environments to navigate through three configuration windows and provide correct answers all along the process in order to configure the connection correctly. Knowledge
required includes if their connection would require a proxy to access the Internet, the IP address of a bridge if required, 
and which pluggable transports are functional in their country.
